---
title: "README"
author: "Bob Rudis"
date: "`r Sys.Date()`"
output:
  md_document:
    variant: markdown_github
---
[![Build Status](https://travis-ci.org/hrbrmstr/punycode.svg)](https://travis-ci.org/hrbrmstr/punycode)

punycode is an R package to work with punycode (RFC3492) domains and relies on the [GNU IDN library](http://www.gnu.org/software/libidn/) for the hard parts.

Tested on Mac OS X & Ubuntu. It _should_ work on Windows provided you install `libidn`. Anyone wanting
to get this officially working on Windows gets accolades beyond imagining. You can install `libidn` on Ubuntu with `sudo apt-get install libidn11-dev` and on OS X with `brew install libidn`. `yum install libidn` seems to work on RedHat/CentOSish systems, too.

The following functions are implemented:

- `puny_encode` : Encode domains
- `puny_deocde` : Decode domains
- `puny_tld_validate` : Validate charset of domains (i.e. is allowed in TLD)
- `is_idna` : Test if a domain is IDNA encoded
- `is_punycode` : Test if a domain is Punycode encoded

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/punycode")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r}
library(punycode)

# current verison
packageVersion("punycode")

ascii_doms <- c("xn------qpeiobbci9acacaca2c8a6ie7b9agmy.net",
"xn----0mcgcx6kho30j.com",
"xn----9hciecaaawbbp1b1cd.net",
"xn----9sbmbaig5bd2adgo.com",
"xn----ctbeewwhe7i.com",
"xn----ieuycya4cyb1b7jwa4fc8h4718bnq8c.com",
"xn----ny6a58fr8c8rtpsucir8k1bo62a.net",
"xn----peurf0asz4dzaln0qm161er8pd.biz",
"xn----twfb7ei8dwjzbf9dg.com",
"xn----ymcabp2br3mk93k.com")

intnl_doms <- c("ثبت-دومین.com",
"טיול-לפיליפינים.net",
"бизнес-тренер.com",
"новый-год.com",
"東京ライブ-バルーンスタンド.com",
"看護師高収入-求人.net",
"ユベラ-贅沢ポリフェノール.biz",
"เด็ก-ภูเก็ต.com",
"ایران-هاست.com")


for_valid <- c("gr€€n.no", "זגורי-אימפריה-לצפייה-ישירה.net", "ثبت-دومین.com",
"טיול-לפיליפינים.net", "xn------qpeiobbci9acacaca2c8a6ie7b9agmy.net", "xn----0mcgcx6kho30j.com",
"xn----9hciecaaawbbp1b1cd.net", "rudis.net")

puny_encode(ascii_doms)

puny_decode(intnl_doms)

puny_tld_check(for_valid)

is_punycode(c("gr€€n.no", "זגורי-אימפריה-לצפייה-ישירה.net", "ثبت-دومین.com",
"טיול-לפיליפינים.net", "xn------qpeiobbci9acacaca2c8a6ie7b9agmy.net", "xn----0mcgcx6kho30j.com",
"xn----9hciecaaawbbp1b1cd.net", "rudis.net"))

is_idna(c("gr€€n.no", "זגורי-אימפריה-לצפייה-ישירה.net", "ثبت-دومین.com",
"טיול-לפיליפינים.net", "xn------qpeiobbci9acacaca2c8a6ie7b9agmy.net", "xn----0mcgcx6kho30j.com",
"xn----9hciecaaawbbp1b1cd.net", "rudis.net"))

```

### Test Results

```{r}
library(punycode)
library(testthat)

date()

test_dir("tests/")
```

